---
title: "Lab 09 - Predictive modeling"
author: |
        | Insert team name here:
        | Insert team member 1 here
        | Insert team member 2 here
        | Insert team member 3 here
        | Insert team member 4 here
date: "Insert date here"
output: pdf_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
# Read in Data
train.appts <- read.csv('http://www.math.montana.edu/ahoegh/teaching/stat408/datasets/MedApptsTrain.csv')
test.appts <- read.csv('http://www.math.montana.edu/ahoegh/teaching/stat408/datasets/MedApptsTest.csv')

# Recode outcome variable to 
# 1 = Missed appointment, 0 = Did not miss appointment
train.appts$No.show <- as.numeric(train.appts$No.show == "Yes")
test.appts$No.show <- as.numeric(test.appts$No.show == "Yes")
```

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.

### Exercise 2

...

### Exercise 3

...

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

Replace "blank1" and "blank2" in the equations below with the appropriate coefficient values.

Linear on the logit (log-odds) scale:
$$
\log\left(\frac{\hat{p}}{1-\hat{p}}\right) = blank1 + blank2*Age
$$
Logistic curve on the probability scale:
$$
\hat{p} = \frac{\exp(blank1 + blank2*Age)}{1 + \exp(blank1 + blank2*Age)}
$$


### Exercise 8

...

### Exercise 9

...

### Exercise 10: Extra Credit

...


